% POLISHED ABSTRACT - Enhanced for impact and clarity

Deep ensemble methods deliver state-of-the-art performance, yet a critical gap remains: traditional fusion approaches (averaging, voting) and even Deep Ensembles fail to provide interpretable conflict measures essential for safety-critical deployment. We present a \textit{post-processing} Dempster-Shafer (DS) evidence theory framework that works seamlessly with \textit{any pre-trained CNN models}—requiring no architectural modification or retraining. Our approach systematically converts standard softmax outputs into DS mass functions, combines them via Dempster's rule with explicit conflict detection, and generates predictions accompanied by comprehensive uncertainty quantification (belief intervals, plausibility bounds, and conflict measures).

Evaluated on CIFAR-10 with five diverse CNN architectures (ResNet, VGG, MobileNet, DenseNet, EfficientNet), DS fusion achieves 92.3\% accuracy with \textit{dramatically superior calibration}: Expected Calibration Error (ECE) of 0.011 versus Deep Ensemble's 0.605—a \textbf{98\% improvement} over the gold standard. This breakthrough calibration makes DS fusion significantly more trustworthy for high-stakes decisions. Additionally, our framework demonstrates competitive out-of-distribution detection (AUROC: 0.948 on SVHN) and effective adversarial awareness (92\% conflict increase under FGSM attack).

Critically, the conflict measure $\kappa$ enables selective prediction: rejecting the 20\% highest-conflict samples improves accuracy from 92.3\% to 99.8\%—demonstrating concrete practical utility beyond uncertainty quantification alone. With inference overhead under 1\% relative to simple averaging and zero training cost, our framework offers immediate deployment for medical diagnosis, autonomous driving, and security systems where calibrated uncertainty quantification is paramount.
