\documentclass[11pt,twocolumn]{article}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage[margin=0.75in]{geometry}
\usepackage{epstopdf}
\usepackage{subcaption}

\begin{document}

\title{Adaptive Multi-Model Ensemble Fusion with Dempster-Shafer Theory for Robust Image Classification}

\author{Anonymous Author\\
Department of Computer Science, University\\
City, Country\\
\texttt{email@university.edu}}

\maketitle

\begin{abstract}
Ensemble learning achieves state-of-the-art performance in deep learning, yet traditional fusion methods (averaging, voting) fail to quantify uncertainty or detect model conflicts—critical for safety-critical applications. We propose a novel Dempster-Shafer (DS) evidence theory-based ensemble framework that provides principled evidence combination with comprehensive uncertainty quantification. Our approach converts CNN softmax outputs to DS mass functions, combines them via Dempster's rule with conflict detection, and generates predictions with interpretable uncertainty metrics (belief, plausibility, doubt). On CIFAR-10 with five diverse CNNs (ResNet, VGG, MobileNet, DenseNet), DS fusion achieves 92.3\% accuracy (vs. 91.5\% averaging, 91.2\% voting). Critically, incorrect predictions exhibit 0.36 higher conflict ($p < 0.001$), validating uncertainty quantification. We demonstrate robust out-of-distribution detection (AUROC 0.94 on SVHN) and increased uncertainty under adversarial attacks. With $<$1\% computational overhead, our framework enables reliable deployment in medical diagnosis, autonomous driving, and security systems.
\end{abstract}

\noindent\textbf{Keywords:} Dempster-Shafer theory, evidence theory, ensemble learning, uncertainty quantification, image classification, CIFAR-10, deep learning

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction}

\section{Related Work}
\label{sec:related}
\input{sections/related_work}

\section{Methodology}
\label{sec:methodology}
\input{sections/methodology}

\section{Experimental Setup}
\label{sec:experiments}
\input{sections/experiments}

\section{Results and Analysis}
\label{sec:results}
\input{sections/results}

\section{Discussion}
\label{sec:discussion}
\input{sections/discussion}

\section{Conclusion}
\label{sec:conclusion}
\input{sections/conclusion}

\bibliographystyle{plain}
\bibliography{references}

\end{document}
